A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-07-15 paper.tex
Always use Tangle while referring the network
Refactor Chap 5 launch data product

\begin{abstract} 
%cite IoT data subscription economy
On top of subscription-based pricing models such as Software-as-a-Service (SaaS), monetizing the subscription enables the payment of data streams with data usage instead of a particular price for a fixed data set. This pricing model allows data providers to have a better vision of managing budgets and data consumers to have the flexibility to subscribe and unsubscribe. However, unlike static data sets, the streaming data increases the importance and difficulties of dynamic data ownership and identity verification. Using certificate authorities (CAs) in such diverse nature for identity verification exposes vulnerabilities of central services, which eventually threatens the trust foundation of the entire system. Therefore, a trustless data trading infrastructure is required where the entities can trade, validate data ownership and data integrity without trusting any service or participants. Besides, consider handling the jobs and trading processes at the same time is too heavy for low-level IoT devices, an automated subscription procedures is also required. In this paper, we leverage usages of distributed ledger technologies (DLTs) to construct a decentralized and trusted data trading platform on top of the IoT brokered infrastructure. This approach can efficiently enhance the degree of transparency and scalability. The storage via an end-to-end encrypted message streams allows transmitting, accessing and validating data streams over distributed ledgers without authorities, and the trading process is automated through smart contracts.
\end{abstract}

@@

Taking all the requirements and the features of streaming data into consideration, the data trading platform for IoT towards a decentralized and trustless design. In this paper, we investigate the use of decentralized publish/subscribe (pub/sub) model and DLTs to construct the authority-less and trusted infrastructure. See Fig.~\ref{fig:system_design}. The pub/sub model features the scalability and resource-efficiency, and DLTs resolve the trust of the service, since data and contracts (i.e., smart contracts) written on DLTs are transparent, immutable, and enforced automatically, which allows devices focus on their jobs while gaining the rewards. Lastly, an end-to-end encrypted transmission protocol built on top of DLT is used as data storage, which not only ensures the data integrity, but also enables access control and provides a scalable key and data management.

@@

In the following researches, Masked Authenticated Messaging (MAM)\cite{MAM} is regarded as a secure data transmission layer and data storage built on top of DLT which provides access control, tamper-proof and authentication functionalities by tailoring messages to a channel. The industrial data marketplace\cite{IOTAIdustryMarketplace} proposed by IOTA Foundation targets for IoT data streams trading in IOTA token, and applies MAM as the data storage and data transmission layer. The decentralized data marketplace in \cite{DDMSmartCities} is fully decentralized without any intermediate server but data providers only, data providers attach and trade data streams via MAM. Nevertheless, the works above does not take into account the refund and unsubscribe mechanism of trading model.

@@

\subsection{Choice of Data Storage}
Data storage is the trust basis of data trading platforms where the data assets are reserved. Streaming data unlike a fixed set of data which can be verified by the hash of whole pack of data, it consists of continually granular records of each time slots. Therefore, the verification such as, data integrity and source identity are narrow down to a data point as well. In our proposed architecture, we adopt MAM as data storage to resolve the challenges of managing and verifying data streams. MAM is the second layer data communication protocol built on top of IOTA\cite{IOTAwhitepaper} network, the Tangle, a feeless cryptocurrency designed for IoT, which introduces properties like publishing, classifying and tracking authenticated message streams. In our work, MAM build the trust of the platform while meeting the requirements of IoT streaming data storage which can be concluded: 1.) \textbf{Scalability}, for both data providers and consumers, MAM keeps the number of managed keys and data entry points as small as possible. 2.) \textbf{Integrity}, messages are written on the Tangle network that are not immutable. 3.) \textbf{Confidentiality}, the message can be encrypted with an \textbf{encryption key} that restricts only authorized players can access contents. 4.) \textbf{Proof of Ownership}, signing messages with \textbf{signature key} generated from Merkle signature scheme\cite{MSS} (MSS) allows users to ensure them originated from the same source by validating the signatures without knowing the actual contents. See Fig.~\ref{fig:channel_and_key} for illustration.

@@

However, the performance results of MAM operations, in Section.\ref{section:mam_performance} show that operating MAM costs a lot of resources for the devices, therefore, we present an alternative solution for data providers to delegate these computing tasks to powerful proxy servers, Tangle-accelerator\cite{TA}, while ensuring the privacy. The details would be further illustrated in Section.\ref{section:ta_endpoint}.

@@

\subsection{Delegate MAM operations to Tangle-accelerator}
\label{section:ta_endpoint}
MAM builds a secure and authenticated communication protocol on top of multiple cryptosystems, which low-level devices need to spend a lot of resources to apply it, and they may not even support built-in libraries in regular operating system. To overcome these concerns, we propose another approach that allows data providers to delegate the MAM operations to Tangle-accelerators, proxy servers with high computation power, which can accelerates the interactions with Tangle while ensuring the privacy of data providers. Fig.~\ref{fig:delegation} shows how data providers can adopt MAM.

\begin{figure}[!t]
    \centering
    \includegraphics[width=\linewidth]{delegation}
    \caption{Data providers can use MAM in 2 ways: the provider performs MAM operations locally, and the provider delegates MAM operations to Tangle-accelerator.}
    \label{fig:delegation}
\end{figure}

@@

\subsubsection{Issues in End-to-End-Encryption}
E2EE helps a lot for low-level edge device utilizing blockchain service. It dramatically reduces execution time encryption takes. However, there are some challenges in the E2EE process. Tampering the messages which have conducted E2EE would be a challenging mission. However, spamming would be the critical issue participants may meet under this architecture. It is risky for an edge device connects to a tangle-accelerator which is operated by unknown third-party. Sharing Channel Chain ownership with an unknown third-party would allow them to spam on the MAM Channel Chain. Spam would cause subscribers wasting plenty of time on decrypting useless messages. To prevent edge devices from the annoying attack, connecting to an known, trustworthy tangle-accelerator would be the easiest solution.

\section{Decentralized Subscription-based Data Trading Case Study}
\label{section:trading_model}
In this section, we illustrate how participants can join the data subscription platform, start subscribing, cancel subscription, and request refund.

@@

\subsection{Launch Data Products}
To launch a data product, data providers need to create a MAM channel/endpoint for data streams and a Product Contract. For those resource-constraint IoT devices, the MAM related operations can be delegated to Tangle-accelerator, as mentioned in Section.~\ref{section:ta_endpoint}. And brokers are responsible for Product Contract creation.

The details of data product, such as data price, MAM channel/endpoint ID and the length of data stream are listed on the Product Contract. As regard to the encryption key of data product, brokers are asked to  record encryption keys to smart contracts. To record encryption key to smart contract, data provider computes the digest of sensitive contents with hash function, and sends the digest as well as the signature to brokers. Broker can first verify the signature from data provider with the public key on DID document. If it's valid, then the broker uploads the key, otherwise the process will be aborted. Note that the broker needs to sign the messages he/she receives, which has been proven to be key uploaded by a broker recorded on the Product Contract. The number of key uploading time is also restricted in order to avoid data provider uploading fake key frequently. If the data consumers find out the encryption key does not match the signature or can not decrypt data streams as expected, they can launch a vote refund to withdraw their funds. Fig.~\ref{fig:key_upload} demonstrates the key uploading process to Product Contract via a broker, and the overall workflow is shown in Fig.~\ref{fig:launching_product}. Finally, the data product is launched and data providers can start uploading data.
\begin{figure}[h]
    \centering
    \includegraphics[width=3.5in]{key_upload}
    \caption{To add encryption key to Product Contract, the data provider sends the digest of encryption key and the one that signed with his/hers private key. After the broker receive the request, he/she performs digital signature as well, then write the result to the Product Contract.}
    \label{fig:key_upload}
\end{figure}

\begin{figure}[!t]
    \centering
    \includegraphics[width=2.5in]{launching_product}
    \caption{The process of launching a product.}
    \label{fig:launching_product}
\end{figure}

@@

Fig.~\ref{fig:mam_create} shows the results of channel/endpoint creation. The time duration for each \textit{height} is the average time of running 100 rounds. Since the creation of channel and endpoint are MSS calculations, the curves of the same hardware are nearly identical. On the other hand, the performance of Raspberry Pi 3 is acceptable when \textit{height} is smaller than 4, but time grows rapidly when \textit{height} is 5 or above. And the performance of PC remains acceptable even \textit{height} gets to 7. The results indicate that MAM channel/endpoint creation is a laborious job for a Raspberry Pi 3 when data providers need a longer channel/endpoint, which is one of the reason that MAM operations should be forwarded to brokers.
\begin{figure*}[!htb]
\minipage{0.32\textwidth}
  \includegraphics[width=\linewidth]{mam_create}
  \caption{Time cost of MAM creation.}\label{fig:mam_create}
\endminipage\hfill
\minipage{0.32\textwidth}
  \includegraphics[width=\linewidth]{mam_send}
  \caption{The probability distributed function of time cost for sending a message through MAM.}\label{fig:mam_send}
\endminipage\hfill
\minipage{0.32\textwidth}%
  \includegraphics[width=\linewidth]{rpi3_pow}
  \caption{Local PoW vs. Remote PoW vs. E2EE}\label{fig:rpi3_pow}
\endminipage
\end{figure*}

@@

Transferring MAM operations to brokers while ensuring the profit and privacy of providers through blind signatures can effectively solve performance problems and lower the threshold to participate in such framework. Brokers can be PCs or powerful machines that runs Ethereum client and Tangle-accelerator, where Ethereum client is used to interact with Ethereum and Tangle-accelerator provides PoW acceleration and MAM delegation. Fig.~\ref{fig:rpi3_pow} shows the time cost of sending a MAM message with 500 bytes payload with local Pow on Raspberry Pi 3, remote Pow on Tangle-accelerator and E2EE on Raspberry Pi 3. However, MAM operations are fairly time-consuming that improving the performance of MAM is an essential issue that needs to be done for the next step.

@@

\subsubsection{Experiment}
PoW, sending to IOTA full node and creating channel these three steps take most of the time to broadcast a MAM message. Applying remote PoW greatly reduces the elapsed time. To improve MAM into a reliable solution for low-level devices, channel creation is the next primary barrier should be removed. With employing delegated MAM and E2EE, MAM channel creation would be delegated to Tangle-accelerator which dramatically enhances the efficiency and makes MAM available for low-level devices. What follows is the performance comparison between MAM and delegated MAM for different payload sizes. Elapsed time for internet communication and PoW are not included, because the processes after sending messages to Tangle-accelerator are the common steps. Excluding the common steps allows us to compare the performance between MAM and delegated MAM more clearly. In addition, MAM channel creation and E2EE asymmetric key pair generation are not included, too, because the two operations would seldom be executed. In the E2EE protocol, we choose SHA-256 for HMAC, AES-CBC for symmetric encryption and Curve P-256 for ECDSA, respectively.

The steps counted in MAM benchmark including:
\begin{enumerate}
    \item Write key information in header
	\item Write and encrypt input payload
	\item Publish final message on IOTA Tangle
\end{enumerate}

The steps counted in delegated MAM (E2EE) benchmark including:
\begin{enumerate}
	\item Generate symmetric key for encryption
	\item Hash input payload
	\item Encrypt input payload
	\item Transmit final message to tangle-accelerator
\end{enumerate}

\begin{table}[htbp]
	\caption{Compare the performance between MAM and E2EE on Raspberry Pi}
    \label{tab:mam_vs_e2ee}
    \centering
        \begin{tabular}{|c||c|c|}
        \hline
            \textbf{size (bytes)} & \textbf{MAM(ms)} & \textbf{E2EE(ms)} \\
            \hline
            100 & 20.28 & 9.21 \\ 
            500 &  26.92 & 9.27 \\ 
            900 & 32.02 &  9.35  \\ 
            1300 & 36.67 & 9.41 \\ 
            1700 & 40.55 & 9.54 \\
            \hline
        \end{tabular}
\end{table}

@@

Table~\ref{tab:mam_vs_e2ee} is the experiment result of the two methods. Eq.~\ref{lin_mam},~\ref{lin_e2ee} are the linear equations for the experiment data of MAM and E2EE respectively. The result reveals elapsed time of E2EE is obviously less than elapsing time of MAM which shows the E2EE process presented in the paper is a much more appropriate solution for resource-constrained systems to send authenticated streaming data. The slope of the result of E2EE is much more flat than the result of MAM which ensures E2EE can consistently perform in an acceptable time range.

@@

However, this work has a main focus on the subscription-based model and relative experiment. Therefore, the next step is to extend the work to:
\begin{enumerate}
	\item reduce the use of Gas in key exchange process and consider the possibility of the zero-knowledge protocol to lower transaction costs
	\item analyze the minimum number of brokers needed for the system and the procedures of the refund mechanism
	\item develop a searching engine for consumers to find their interested tagging or data products as well as a ranking system to maintain the quality.
\end{enumerate}

>>>>

\begin{abstract} 
%cite IoT data subscription economy
On top of subscription-based pricing models such as Software-as-a-Service (SaaS), monetizing the subscription enables the payment of data streams with data usage instead of a particular price for a fixed data set. This pricing model allows data providers to have a better vision of managing budgets and data consumers to have the flexibility to subscribe and unsubscribe. However, unlike static data collections, the streaming data increases difficulties of dynamic data ownership and identity verification. A trustless data trading infrastructure is required where the entities can trade, validate data ownership and data integrity without trusting any service or participants. In addition, an automated subscription procedure is also demanded for the sake of data monetization. In this paper, we leverage usages of distributed ledger technologies (DLTs) to construct a decentralized data trading platform on top of the IoT brokered infrastructure. This approach can efficiently enhance the degree of transparency and scalability. The storage built upon cryptographic message protocols allows transmitting, accessing and validating data streams over distributed ledgers without authorities, and the digital rights of trading participants deserve a guarantee, which is enabled by design.
\end{abstract}

@@

Taking all the requirements into consideration, we investigate the use of decentralized publish/subscribe (pub/sub) model and DLTs to construct the authority-less and trusted infrastructure as shown in Fig.~\ref{fig:system_design}. The pub/sub model features the scalability and resource-efficiency, and DLTs resolve the trust of the service, since data and contracts written on DLTs are transparent, immutable, and enforced automatically, which allows devices focus on their jobs while gaining the rewards. Lastly, an end-to-end encrypted transmission protocol built on top of DLT is used as data storage, which not only ensures the data integrity, but also enables access control and provides a scalable key and data management.

@@

In the following researches, Masked Authenticated Messaging (MAM)\cite{MAM} is regarded as a secure data transmission layer and data storage built on top of DLT which provides access control, tamper-proof and authentication functionalities by tailoring messages to a channel. The industrial data marketplace\cite{IOTAIdustryMarketplace} proposed by IOTA Foundation targets for IoT data streams trading in IOTA token, and applies MAM as the data storage and data transmission layer. The decentralized data marketplace \cite{DDMSmartCities} is operated without any intermediate server but data providers only, data providers attach and trade data streams via MAM. Nevertheless, the above works did not take into account the refund and unsubscribe mechanism of trading model.

@@

\subsection{Choice of Data Storage}
Data storage is the trust basis of data trading platforms where the data assets are reserved. Streaming data unlike a fixed set of data which can be verified by the hash of whole pack of data, it consists of continually granular records of each time slots. Therefore, the verification such as, data integrity and source identity are narrow down to a data point as well. In our proposed architecture, we adapt MAM as data storage to resolve the challenges of managing and verifying data streams. MAM is the second layer data communication protocol built on top of IOTA network, the Tangle, a feeless cryptocurrency designed for IoT, which introduces properties like publishing, classifying and tracking authenticated message streams. In our work, MAM build the trust of the platform while meeting the requirements of IoT streaming data storage which can be concluded: 1) \textbf{Scalability}, for both data providers and consumers, MAM keeps the number of managed keys and data entry points as small as possible. 2) \textbf{Integrity}, messages written on the Tangle are immutable. 3) \textbf{Confidentiality}, the message can be encrypted with an \textbf{encryption key} that restricts only authorized players can access contents. 4) \textbf{Proof of Ownership}, signing messages with \textbf{signature key} generated from Merkle signature scheme\cite{MSS} (MSS) allows users to ensure them originated from the same source by validating the signatures without knowing the actual contents. See Fig.~\ref{fig:channel_and_key} for illustration.

@@

However, the performance results of MAM operations, in Section.\ref{section:mam_performance} show that operating MAM costs a lot of resources for the devices, therefore, we present an alternative solution for data providers to delegate these computing tasks to powerful proxy servers, Tangle-accelerator (Accel)\cite{TA}, while ensuring the privacy. The details would be further illustrated in Section.\ref{section:ta_endpoint}.

@@

\subsection{Delegate MAM operations to Accel}
\label{section:ta_endpoint}
MAM builds a secure and authenticated communication protocol on top of multiple cryptosystems, which low-level devices need to spend a lot of resources to apply it, and they may not even support built-in libraries in regular operating system. To overcome these concerns, we propose another approach that allows data providers to delegate the MAM operations to Accel, proxy servers with high computation power, which can accelerates the interactions with Tangle while ensuring the privacy of data providers. Fig.~\ref{fig:delegation} shows how data providers can adopt MAM.

\begin{figure}[!t]
    \centering
    \includegraphics[width=\linewidth]{delegation}
    \caption{Data providers can use MAM in 2 ways: the provider performs MAM operations locally, and the provider delegates MAM operations to Accel.}
    \label{fig:delegation}
\end{figure}

@@

\subsubsection{Issues in End-to-End-Encryption}
E2EE helps a lot for low-level edge device utilizing blockchain service. It dramatically reduces execution time encryption takes. However, there are some challenges in the E2EE process. Tampering the messages which have conducted E2EE would be a challenging mission. However, spamming would be the critical issue participants may meet under this architecture. It is risky for an edge device connects to a Accel which is operated by unknown third-party. Sharing Channel Chain ownership with an unknown third-party would allow them to spam on the MAM Channel Chain. Spam would cause subscribers wasting plenty of time on decrypting useless messages. To prevent edge devices from the annoying attack, connecting to an known, trustworthy Accel would be the easiest solution.

\section{Decentralized Subscription-based Data Trading Models}
\label{section:trading_model}
In this section, we illustrate how participants can join the data subscription platform, start subscribing, cancel subscription. A discussion of refund is illustrated.

@@

\subsection{Launch Data Products}
To launch a data product, brokers are responsible to create Product Contract and record the metadatas of data product for data providers. The Product Contract will not accept subscriptions until brokers certify the encryption key. To certify the encryption key, the data provider first computes its digest with hash function, and sends the digest as well as the signature to brokers. The broker verify the signature with the public key on provider's DID document. If it's valid, the broker will sign and upload the key to Product Contract, otherwise the process will be aborted. The number of key uploading time is restricted in order to avoid data provider uploading fake keys frequently. If data consumers find out the encryption key does not match the provider's signature after payment, they can request a refund. Fig.~\ref{fig:key_upload} demonstrates the key uploading process to Product Contract via a broker. Finally, the data product is launched and data providers can start uploading data.
\begin{figure}[h]
    \centering
    \includegraphics[width=3.5in]{key_upload}
    \caption{To add encryption key to Product Contract, the data provider sends the digest of encryption key and the one that signed with his/hers private key. After the broker receive the request, he/she signs it as well, then write the result to the Product Contract.}
    \label{fig:key_upload}
\end{figure}

@@

Fig.~\ref{fig:mam_create} shows the results of channel/endpoint creation. The time duration for each \textit{height} is the average time of running 100 rounds. Since the creation of channel and endpoint are MSS calculations, the curves of the same hardware are nearly identical. On the other hand, the performance of RPi is acceptable when \textit{height} is smaller than 4, but time grows rapidly when \textit{height} is 5 or above. And the performance of PC remains acceptable even \textit{height} gets to 7. The results indicate that MAM channel/endpoint creation is a laborious job for a RPi when data providers need a longer channel/endpoint, which is one of the reason that MAM operations should be forwarded to brokers.
\begin{figure*}[!htb]
\minipage{0.32\textwidth}
  \includegraphics[width=\linewidth]{mam_create}
  \caption{Time cost of MAM creation.}\label{fig:mam_create}
\endminipage\hfill
\minipage{0.32\textwidth}
  \includegraphics[width=\linewidth]{mam_send}
  \caption{The probability distributed function of time cost for sending a message through MAM.}\label{fig:mam_send}
\endminipage\hfill
\minipage{0.32\textwidth}%
  \includegraphics[width=\linewidth]{rpi3_pow}
  \caption{Local PoW vs. Remote PoW vs. E2EE}\label{fig:rpi3_pow}
\endminipage
\end{figure*}

@@

Transferring MAM operations to brokers while ensuring the profit and privacy of providers through blind signatures can effectively solve performance problems and lower the threshold to participate in such framework. Brokers can be PCs or powerful machines that runs Ethereum client and Accel, where Ethereum client is used to interact with Ethereum, and Accel provides PoW acceleration and MAM delegation. Fig.~\ref{fig:rpi3_pow} shows the time cost of sending a MAM message with 500 bytes payload with local PoW on RPi, remote PoW on Accel and E2EE on RPi. However, MAM operations are fairly time-consuming that improving the performance of MAM is an essential issue that needs to be done for the next step.

@@

\subsubsection{Experiment}
PoW, sending to IOTA full node and creating channel these three steps take most of the time to broadcast a MAM message. Applying remote PoW greatly reduces the elapsed time. To improve MAM into a reliable solution for low-level devices, channel creation is the next primary barrier should be removed. With employing delegated MAM and E2EE, MAM channel creation would be delegated to Accel which dramatically enhances the efficiency and makes MAM available for low-level devices. What follows is the performance comparison between MAM and delegated MAM for different payload sizes. Elapsed time for internet communication and PoW are not included, because the processes after sending messages to Accel are the common steps. Excluding the common steps allows us to compare the performance between MAM and delegated MAM more clearly. In addition, MAM channel creation and E2EE asymmetric key pair generation are not included, too, because the two operations would seldom be executed. In the E2EE protocol, we choose SHA-256 for HMAC, AES-CBC for symmetric encryption and Curve P-256 for ECDSA, respectively.

The steps counted in MAM benchmark including:
\begin{enumerate}
    \item Write key information in header
	\item Write and encrypt input payload
	\item Publish final message on Tangle
\end{enumerate}

The steps counted in delegated MAM (E2EE) benchmark including:
\begin{enumerate}
	\item Generate symmetric key for encryption
	\item Hash input payload
	\item Encrypt input payload
	\item Transmit final message to Accel
\end{enumerate}

\begin{table}[htbp]
	\caption{Compare the performance between MAM and E2EE on RPi}
    \label{tab:mam_vs_e2ee}
    \centering
        \begin{tabular}{|c||c|c|}
        \hline
            \textbf{size (bytes)} & \textbf{MAM(ms)} & \textbf{E2EE(ms)} \\
            \hline
            100 & 20.28 & 9.21 \\ 
            500 &  26.92 & 9.27 \\ 
            900 & 32.02 &  9.35  \\ 
            1300 & 36.67 & 9.41 \\ 
            1700 & 40.55 & 9.54 \\
            \hline
        \end{tabular}
\end{table}

@@

Table~\ref{tab:mam_vs_e2ee} is the experiment result of the two methods. Eq.~\ref{lin_mam},~\ref{lin_e2ee} are the linear equations for the experiment data of MAM and E2EE respectively. The result reveals elapsed time of E2EE is obviously less than elapsing time of MAM which shows the E2EE process presented in the paper is a much more appropriate solution for resource-constrained systems to send authenticated streaming data. The slope of the result of E2EE is much more flat than the result of MAM which ensures E2EE can consistently perform in an acceptable time range. Under our design which delegate MAM operations with Accel and the presented E2EE protocol, data provider can include resource-constrained hardware into the data subscription economy. E2EE protocol promises tamperless data transmission, and only authorized subscribers can read the encrypted information.

@@

However, this work has a main focus on the subscription-based model and relative experiments. Consequently, the next step is extending the work to:
\begin{enumerate}
	\item reduce the use of Gas in key exchange process and consider the possibility of the zero-knowledge protocol to lower transaction costs
	\item analyze the minimum number of brokers needed for the system and the procedures of the refund mechanism
	\item develop a searching engine for consumers to find their interested tagging or data products as well as a ranking system to maintain the quality.
\end{enumerate}

Finally, a decentralized model enables the data stream trading by shifting risks, and correspondingly, the digital rights of its participants deserve a guarantee, which is provided with the automated system.
